|

### 2020-12-07 appendix/appendix.Rmd
commit 2 12/06

Most papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`). The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[1])`). Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`). As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[2]`, while the number of papers is only `r length(unique(dat$id))`.

@@

```{r, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)

mod1 <- tibble(
     ` ` = c("Intercept",
             "Indepvar: N",
             "Indepvar: logN",
             "Year",
             "Elecsys: Non-Majoritarian",
             "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "PCTGDP"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 4)))
```

@@

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod

mod1_permu <- tibble(
     ` ` = c("Intercept",
             "Indepvar: N",
             "Indepvar: logN",
             "Year",
             "Elecsys: Non-Majoritarian",
             "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)

mod2 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Indepvar: logN",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod

mod2_permu <- tibble(
     ` ` = c("Intercept",
             "Indepvar: N",
             "Indepvar: logN",
             "Year",
             "Elecsys: Non-Majoritarian",
             "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "PCTGDP - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, error=F, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear,
            control=list(maxiter=1000))

mod3 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

```{r, warning=F, cache=T}
summary(mod)
```
As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, error=F, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod

mod3_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)

mod4 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F, iter = 100)
mod

mod4_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)

mod5 <- tibble(
   ` ` = c("Intercept",
           "Indepvar: N",
           "Year",
           "Published: No",
           "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod

mod5_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Method: Panel"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "logExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))

mod5_permu %>%
  select(-model) %>%
  kable(booktabs = T,align = "c",linesep ='') %>%
  kable_styling(c("striped","bordered"), position = "center")
```

We have the following results for the meta-regressions of Log of Expenditure Per Capita:

1. Unpublished papers report significantly higher coefficients.
2. Moving from `OLS` to `PANEL` increases the detected effects.
3. All other coefficients remained insignificant.

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)

mod6 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Method: Panel",
          "Method: RDD"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F)

mod6_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Method: Panel",
          "Method: RDD"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4), ")"),
  model = "logExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

>>>>

Most papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(dat$indepvar2)[2])`). The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(dat$indepvar2)[1])`). Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(dat$indepvar2)[3])`). As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[1]`, while the number of papers is only `r length(unique(dat$id))`.

@@

```{r, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)
summary(mod)
```

@@

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)
summary(mod)
```

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod
```

@@

```{r, error=F, warning=F, cache=T}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear,
            control=list(maxiter=1000))
summary(mod)
```
As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, error=F, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)
summary(mod)
```

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F, iter = 100)
mod
```

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)
```

@@

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
mod
```

Gor the meta-regressions of Log of Expenditure Per Capita we find no significant results.

@@

```{r, warning=F, cache=T}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)
summary(mod)
```

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F)
```
